Decentralized autonomous organization to manage a trust\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-03-17 paper/Paper.tex

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$. Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut}}[\text{sender}]
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut}}[\text{sender}]$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

@@

    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
    /// with `_newServiceProvider` as the new service provider, as has been
    /// proposed in proposal `_proposalID`. This will burn my tokens. This can
    /// not be undone and will split the DAO into two DAO's, with two
    /// different underlying tokens.
    /// @param _proposalID The proposal ID
    /// @param _newServiceProvider The new service provider of the new DAO
    /// @dev This function, when called for the first time for this proposal,
    /// will create a new DAO and send the sender's portion of the remaining
    /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
    /// of the sender. (TODO: document rewardTokens - done??)
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);

@@

    function setDeploymentFee(uint _deploymentReward) callingRestriction {
        if (deploymentReward > 10 ether && msg.sender != address(client))
            throw; // TODO, set a max defined by service provider, or ideally oracle (set in euro)
        deploymentReward = _deploymentReward;
    }

>>>>

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

@@

    /// @notice ATTENTION! I confirm to move my remaining funds to a new DAO
    /// with `_newServiceProvider` as the new service provider, as has been
    /// proposed in proposal `_proposalID`. This will burn my tokens. This can
    /// not be undone and will split the DAO into two DAO's, with two
    /// different underlying tokens.
    /// @param _proposalID The proposal ID
    /// @param _newServiceProvider The new service provider of the new DAO
    /// @dev This function, when called for the first time for this proposal,
    /// will create a new DAO and send the sender's portion of the remaining
    /// ether and Reward Tokens to the new DAO. It will also burn the DAO Tokens
    /// of the sender. 
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);

@@

    function setDeploymentFee(uint _deploymentReward) callingRestriction {
        if (deploymentReward > 10 ether && msg.sender != address(client))
            throw; 
        deploymentReward = _deploymentReward;
    }
